A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-08 paper.Rmd
working on section 5.1

Figure \ref{fig:polypower} displays the estimated power of a visual test, computed on evaluations of the lineups generated by the non-linearity model with uniform fitted values. Power is plotted against the natural logarithm of the effect size $log_e(E)$, computed at a 5% significance level. The small plots at the bottom of this figure shows a sequence of example residual plots of increasing effect size. These are for the readers to compare what a residual plot might look like at particular effect sizes.

>>>>

Figures \ref{fig:polypower} and \ref{fig:heterpower} present the power curves of various tests plotted against the effect size in the residuals. The effect size was computed at a 5% significance level and plotted on a natural logarithmic scale. To facilitate visual calibration of effect size values with the corresponding diagnostic plots, a sequence of example residual plots with increasing effect sizes is provided at the bottom of these figures. These plots serve as a visual aid to help readers understand how different effect size values translate to changes in the diagnostic plots.

displays the estimated power of a visual test, computed on evaluations of the lineups generated by the non-linearity model with uniform fitted values. Power is plotted against the natural logarithm of the effect size $log_e(E)$, computed at a 5% significance level. The small plots at the bottom of this figure shows a sequence of example residual plots of increasing effect size. These are for the readers to compare what a residual plot might look like at particular effect sizes.

### 2023-04-08 paper.tex
working on section 5.1

Figure \ref{fig:polypower} displays the estimated power of a visual
test, computed on evaluations of the lineups generated by the
non-linearity model with uniform fitted values. Power is plotted against
the natural logarithm of the effect size \(log_e(E)\), computed at a 5\%
significance level. The small plots at the bottom of this figure shows a
sequence of example residual plots of increasing effect size. These are
for the readers to compare what a residual plot might look like at
particular effect sizes.

>>>>

Figures \ref{fig:polypower} and \ref{fig:heterpower} present the power
curves of various tests plotted against the effect size in the
residuals. The effect size was computed at a 5\% significance level and
plotted on a natural logarithmic scale. To facilitate visual calibration
of effect size values with the corresponding diagnostic plots, a
sequence of example residual plots with increasing effect sizes is
provided at the bottom of these figures. These plots serve as a visual
aid to help readers understand how different effect size values
translate to changes in the diagnostic plots.

displays the estimated power of a visual test, computed on evaluations
of the lineups generated by the non-linearity model with uniform fitted
values. Power is plotted against the natural logarithm of the effect
size \(log_e(E)\), computed at a 5\% significance level. The small plots
at the bottom of this figure shows a sequence of example residual plots
of increasing effect size. These are for the readers to compare what a
residual plot might look like at particular effect sizes.
